Example Manuscript Template for a Data Analysis Project

### 2025-04-05 products/manuscript/Manuscript.qmd
commit to the changes in the files

```{r}
#| label: model-1
#| fig-cap: "predicted vs observed of three models"
#| echo: FALSE
knitr::include_graphics(here("results","figures","predVSobs.png"))
```
LASSO did not substantially improve performance over linear regression, likely due to a weak regularization effect at the selected penalty. Variable importance from the Random Forest model identified BMI, participants age,lean body mass,CD4+ and sex, with Sex emerging as a minor contributor to CD4 Immune Activation count levels.

>>>>

```{r}
#| label: model-1
#| fig-cap: "predicted vs observed of three models"
#| echo: FALSE
knitr::include_graphics(here("results","figures","Predicted_vs_observed.png"))
```
LASSO did not substantially improve performance over linear regression, likely due to a weak regularization effect at the selected penalty. Variable importance from the Random Forest model identified BMI, participants age,lean body mass,CD4+ and sex, with Sex emerging as a minor contributor to CD4 Immune Activation count levels.
